%-------------------------
% Resume in Latex (Customized for Muhammad Umer)
% Based on Jake Gutierrez Template
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage[sfdefault]{roboto}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muhammad Umer} \\ \vspace{2pt}
    \small +92 315 3271442 $|$ 
    \href{mailto:mumer.2k1@gmail.com}{\underline{mumer.2k1@gmail.com}} $|$
    \href{https://github.com/umer-2k1}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/mumer2001/}{\underline{LinkedIn}} $|$
    \href{https://umer2k1-dev.netlify.app/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Full-Stack Software Engineer (3 years) with expertise in Web and Mobile apps, AI/LLM integrations, and real-time systems. Delivered scalable, revenue-generating products, including a crypto e-commerce platform serving 3,200+ brands across 190+ countries. Skilled in TypeScript, React Native, Next.js, Node.js, NestJS, FastAPI, and modern AI stacks (LangChain, RAG, Agentic AI).


%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} JavaScript, TypeScript, Python \\
\textbf{Frontend:} Next.js, React.js, React Native, TanStack Query, Redux, Zustand, Tailwind, Shadcn UI \\
\textbf{Backend:} Node.js, NestJS, FastAPI \\
\textbf{Databases:} MongoDB, PostgreSQL \\
\textbf{AI/LLM:} OpenAI, LangChain, LangGraph, RAG, Agentic AI, MCP Server \\
\textbf{Cloud \& DevOps:} AWS (EC2, S3), Firebase (Auth, Firestore, FCM), Docker, Vercel \\
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% Sybrid
\resumeSubheading
{Sybrid Private Limited — A Lakson Group Company}{Jul 2025 -- Present}
{Full-Stack Software Engineer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{Leading a React Native iOS medication app with diagnosis modules, increasing adoption across healthcare teams.}
\resumeItem{Implemented CI/CD pipelines using Codemagic, reducing manual release time by 50\%.}
\resumeItem{Managing backend services (Node.js) and Next.js admin panel with secure medical data workflows.}
\resumeItemListEnd

% Kodexolabs
\resumeSubheading
{Kodexolabs}{Oct 2024 -- Jul 2025}
{Full-Stack Software Engineer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{\textbf{Developed a React Native iOS health app} integrating Apple HealthKit, improving data sync reliability by \textbf{25\%}.}
\resumeItem{Built an \textbf{AI-driven nutrition, workout, and wellness system} using \textbf{LangChain + RAG}.}
\resumeItem{Created an \textbf{AI Virtual Trainer} that increased user engagement by \textbf{40\%}.}
\resumeItem{Engineered a \textbf{GPT-Canvas–style streaming text renderer} with \textbf{98\% rendering accuracy}.}
\resumeItem{Built \textbf{SmartHistory} (Next.js + NestJS) — an AI-led medical history intake system. Demo: \href{https://v2.smartmedhx.ai}{smartmedhx.ai}}
\resumeItem{Developed \textbf{Fairness Factor} using Next.js + LangChain Agents — used by \textbf{1,000+ professionals}. App: \href{https://app.fairnessfactor.com/}{fairnessfactor.com}}
\resumeItem{Improved code quality and reduced bugs by \textbf{20\%} through structured code reviews.}
\resumeItemListEnd

% DotClick
\resumeSubheading
{DotClick LLC}{Aug 2023 -- Oct 2024}
{Full-Stack Software Engineer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{Built Refill Arena, a crypto gift card platform generating \$1M+ revenue in its first year.}
\resumeItem{Integrated Coinbase Commerce + MetaMask for secure multi-currency blockchain payments.}
\resumeItem{Developed scalable APIs supporting 3,200+ brands across 190+ countries with 99.9\% uptime.}
\resumeItem{Created a customization platform using React + Fabric.js with realistic mockups and image processing.}
\resumeItem{Built gig-based home cleaning marketplace for 200+ users with chat, reviews, incentives, and worker ranking.}
\resumeItemListEnd

% Askari Technologies
\resumeSubheading
{Askari Technologies}{Dec 2022 -- Jun 2023}
{Full-Stack MERN Developer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{Improved frontend performance by 25\% through optimized state management.}
\resumeItem{Implemented JWT authentication and Stripe payments/subscriptions.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Design Heaven} | React, Fabric.js, FFmpeg, Unsplash API}{}
\resumeItemListStart
\resumeItem{Built poster \& video editor with trimming, merging, text effects, and asset library.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{CryptoCity} | React, CoinGecko API, Chart.js}{}
\resumeItemListStart
\resumeItem{Developed real-time crypto tracker with charting and global price updates.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Dawood University of Engineering \& Technology}{Dec 2020 -- Jul 2024}
{Bachelor of Engineering in Computer System Engineering | CGPA: 3.6}{Karachi, Pakistan}
\resumeSubHeadingListEnd

\end{document}
