%-------------------------
% Resume in Latex (Customized for Muhammad Umer)
% Based on Jake Gutierrez Template
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage[sfdefault]{roboto}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muhammad Umer} \\ \vspace{2pt}
    \small +92 315 3271442 $|$
    \href{mailto:mumer.2k1@gmail.com}{\underline{mumer.2k1@gmail.com}} $|$
    \href{https://github.com/umer-2k1}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/mumer2001/}{\underline{LinkedIn}} $|$
    \href{https://umer2k1-dev.netlify.app/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Senior Full-Stack Developer (3 years) with expertise in Node.js, React.js, and TypeScript. Proven track record of delivering scalable, high-quality products with a strong focus on testing and good HTML/CSS practices.

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Programming Languages:} JavaScript, TypeScript \\
\textbf{Frontend:} React.js, Next.js, HTML/CSS, CSS Preprocessors \\
\textbf{Backend:} Node.js \\
\textbf{Databases:} Relational Databases, MongoDB, PostgreSQL \\
\textbf{Testing:} Unit Testing, Integration Testing \\
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% Sybrid
\resumeSubheading
{Sybrid Private Limited — A Lakson Group Company}{Jul 2025 -- Present}
{Full-Stack Software Engineer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{Developed a React Native application with Node.js backend services.}
\resumeItem{Implemented testing frameworks to ensure high-quality code.}
\resumeItem{Managed and optimized database queries for improved performance.}
\resumeItemListEnd

% Kodexolabs
\resumeSubheading
{Kodexolabs}{Oct 2024 -- Jul 2025}
{Full-Stack Software Engineer}{Karachi, Pakistan}
\resumeItemListStart
\resumeItem{Built a React Native application with a Node.js backend, utilizing TypeScript and relational databases.}
\resumeItem{Implemented testing and validation to ensure high-quality code.}
\resumeItem{Optimized frontend performance using good HTML/CSS practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{React Native App} | React Native, Node.js, TypeScript}{}
\resumeItemListStart
\resumeItem{Developed a mobile application using React Native and Node.js.}
\resumeItem{Implemented testing and validation to ensure high-quality code.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Node.js Backend} | Node.js, Express, TypeScript}{}
\resumeItemListStart
\resumeItem{Built a scalable Node.js backend using Express and TypeScript.}
\resumeItem{Implemented database queries and optimized performance.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
